\documentclass[9pt,a4paper]{article}
\usepackage[margin=1cm,landscape]{geometry}
\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  headheight=1cm,
  top=1cm,
  bottom=1.5cm,
  footskip=1cm,
  %showframe
}

%\usepackage{lipsum}

\usepackage{hyperref} % For hyperlinks
\hypersetup{
    colorlinks=true,
    %linkcolor=blue,
    %filecolor=magenta,
    urlcolor=cyan,
}

\usepackage{multicol} % For overall column layout
\usepackage{xcolor} % For colors
\usepackage{tabularx}
\usepackage{fancyhdr} % For footer

\pagenumbering{gobble} % No page numbering
\pagestyle{fancy}
\fancyhead{} % No header
\renewcommand{\headrulewidth}{0pt} % No header rule

\cfoot{\copyright~2019 Canonical} % Actual footer text

% A bunch of command for boilerplate text
\newcommand{\colconcmd}[1]{\textbf{\sffamily\color{blue}#1}~~}
\newcommand{\colconverb}[1]{{\sffamily\color{blue}#1}~~}   %\verb already defined
\newcommand{\textangles}[1]{\textless #1\textgreater}
\newcommand{\smallhspace}{\-\hspace{0.3cm}}
\newcommand{\terminalfont}[1]{{\sffamily#1}}
\newcommand{\terminal}[1]{\-\hspace{0.5cm}\terminalfont{\$ #1}}
\newcommand{\terminalinebreak}[1]{\ \textbackslash\hfill\phantom{.}\linebreak\-\hspace{0.5cm}~}
\newcommand{\ddash}{-{}-}

\begin{document}
\setlength\parindent{0pt}
\begin{multicols*}{3}[]

\begin{center}
  \textbf{\Large ROS 2 Cheats Sheet}
\end{center}
%

\hrulefill

\textbf{colcon - collective construction}\\
colcon is a command line tool to improve the workflow of building,
testing and using multiple software packages.
It automates the process,
handles the ordering and sets up the environment to use the packages.

All colcon tools start with the prefix `colcon' followed by a command
and (likely) positional/optional arguments.

For any tool, the documentation is accessible with,\\
%
\terminal{colcon \colconcmd{command} \ddash help}\\
%
Moreover, colcon offers auto-completion for all verbs and
most positional/optional arguments. E.g.,\\
%
\terminal{colcon \colconcmd{command} [tab][tab]}

Find out how to enable auto-completion at
\href{https://colcon.readthedocs.io/en/released/index.html}
{colcon's online documentation}.

\hrulefill

Environment variables:\\
%
% \begin{tabularx}{\linewidth}{X}
$\circ$ \terminalfont{CMAKE\_COMMAND}
\smallhspace
The full path to the CMake executable.                                    \\
%
$\circ$ \terminalfont{COLCON\_ALL\_SHELLS}
\smallhspace
Flag to enable all shell extensions.                                      \\
%
$\circ$ \terminalfont{COLCON\_COMPLETION\_LOGFILE}
\smallhspace
Set the logfile for completion time.                                      \\
%
$\circ$ \terminalfont{COLCON\_DEFAULTS\_FILE}
\smallhspace
Set path to the yaml file containing the default values for
the command line arguments (default:\$COLCON\_HOME/defaults.yaml).        \\
%
$\circ$ \terminalfont{COLCON\_DEFAULT\_EXECUTOR}
\smallhspace
Select the default executor extension.                                    \\
%
$\circ$ \terminalfont{COLCON\_EXTENSION\_BLACKLIST}
\smallhspace
Blacklist extensions which should not be used.                            \\
%
$\circ$ \terminalfont{COLCON\_HOME}
\smallhspace
Set the configuration directory (default: ~/.colcon.)                     \\
%
$\circ$ \terminalfont{COLCON\_LOG\_LEVEL}
\smallhspace
Set the log level (debug|10, info|20, warn|30, error|40, critical|50,
or any other positive numeric value).                                     \\
%
$\circ$ \terminalfont{COLCON\_LOG\_PATH}
\smallhspace
Set the log directory (default: \$COLCON\_HOME/log).                      \\
%
$\circ$ \terminalfont{CTEST\_COMMAND}
\smallhspace
The full path to the CTest executable.                                    \\
%
$\circ$ \terminalfont{POWERSHELL\_COMMAND}
\smallhspace
The full path to the PowerShell executable.
%
% \end{tabularx}
%

\hrulefill

Global options:\\
%
$\circ$ \terminalfont{\ddash log-base \textangles{path}}
The base path for all log directories (default: log). \\
%
$\circ$ \terminalfont{\ddash log-level \textangles{level}}
Set log level for the console output, either by numeric or string value (default: warn)

\hrulefill

%
\colconcmd{build} Build a set of packages.
\\
Examples:
\\
Build the whole workspace: \\
\terminal{colcon build} \\
%
Build a single package excluding dependencies: \\
\terminal{colcon build \ddash packages-selected demo\_nodes\_cpp} \\
%
Build two packages including dependencies,
use symlinks instead of copying files where possible and
print immediately on terminal:\\
\terminal{colcon build \ddash packages-up-to demo\_nodes\_cpp
\terminalinebreak~action\_tutorials \ddash symlink-install
\terminalinebreak~\ddash event-handlers console\_direct+}
%

\hrulefill

%
\colconcmd{extension-points} List extension points.
%

\hrulefill

%
\colconcmd{extensions} Package information.
%

\hrulefill

%
\colconcmd{info} List extension points.
%

\hrulefill

%
\colconcmd{list} List packages, optionally in topological ordering.
\\
Example:
\\
List all packages in the workspace:\\
\terminal{colcon list} \\
%
List all packages names in topological order up-to a given package:\\
\terminal{colcon list \ddash names-only \ddash topological-order
\terminalinebreak~\ddash packages-up-to demo\_nodes\_cpp}
%

\hrulefill

%
\colconcmd{metadata} Manage metadata of packages.
%
% \\
%
% Examples:
% \\
% \terminal{todo}

\hrulefill

%
\colconcmd{test} Test a set of packages.
\\
Example:
\\
Test the whole workspace:\\
\terminal{colcon test} \\
%
Test a single package excluding dependencies:\\
\terminal{colcon test \ddash packages-select demo\_nodes\_cpp} \\
%
Test a package including packages that depend on it:\\
\terminal{colcon test \ddash packages-above demo\_nodes\_py} \\
%
Test two packages including dependencies,
and print on terminal:\\
\terminal{colcon test \ddash packages-up-to demo\_nodes\_cpp
\terminalinebreak~demo\_nodes\_py
\ddash event-handlers console\_direct+} \\
%
Pass arguments to pytest (e.g. to print a coverage report):\\
\terminal{colcon test \ddash packages-select demo\_nodes\_cpp
\terminalinebreak~\ddash event-handlers console\_direct+
\terminalinebreak~\ddash pytest-args \ddash cov=sros2}
%

\hrulefill

%
\colconcmd{test-result} Show the test results generated when testing a set of packages.
%
\\
Example:
\\
Show all test results generated, including successful tests:\\
\terminal{colcon test-result \ddash all}
%

\hrulefill

%
\colconcmd{version-check} Compare local package versions with PyPI.
\\
Examples:
\\
\terminal{todo}
%

\hrulefill

Must know colcon flags.

$\circ$ \terminalfont{\ddash symlink-install}
\smallhspace
Use `symlinks' instead of installing (copying) files where possible.

$\circ$ \terminalfont{\ddash continue-on-error}
\smallhspace
Continue other packages when a package fails to build.
Packages recursively depending on the failed package are skipped.

$\circ$ \terminalfont{\ddash event-handlers console\_direct+}
\smallhspace
Show output on console.

$\circ$ \terminalfont{\ddash event-handlers console\_cohesion+}
\smallhspace
Show output on console after a package has finished.

$\circ$ \terminalfont{\ddash packages-select}
\smallhspace
Build only specific package(s).

$\circ$ \terminalfont{\ddash packages-up-to}
\smallhspace
Build specific package(s) and its/their recursive dependencies.

$\circ$ \terminalfont{\ddash packages-above}
\smallhspace
Build specific package(s) and other packages that recursively depending on it.

$\circ$ \terminalfont{\ddash packages-skip}
\smallhspace
Skip package(s).

$\circ$ \terminalfont{\ddash packages-skip-build-finished}
\smallhspace
Skip a set of packages which have finished to build previously.

$\circ$ \terminalfont{\ddash cmake-args}
\smallhspace
Pass arguments to CMake projects.

$\circ$ \terminalfont{\ddash cmake-clean-cache}
\smallhspace
Remove CMake cache before the build (implicitly forcing CMake configure step).

$\circ$ \terminalfont{\ddash cmake-clean-first}
\smallhspace
Build target `clean' first, then build (to only clean use '--cmake-target clean').

$\circ$ \terminalfont{\ddash cmake-force-configure}
\smallhspace
Force CMake configure step.

\end{multicols*}
\end{document}
